A matrix-free approach for finite-strain hyperelastic problems using geometric multigrid

### 2018-09-18 doc/large_strain.tex
acknowledgements

>>>>

\section*{Acknowledgements}

DD acknowledge the financial support of the German Science Foundation (Deutsche Forschungs-Gemeinschaft, DFG), grant DA 1664/2-1
and the Competence Network for Technical and Scientific High Performance Computing in Bavaria (KONWIHR).
DD, DA and JPP are grateful to Jed Brown (CU Boulder) and Veselin Dobrev (Lawrence Livermore National Laboratory) for a fruitful discussion on matrix-free operator evaluation approaches.
%
{\color{red}
DA was supported ...
%
JPP was supported by ...
}
%
PS acknowledges the support of the Cluster of Excellence Engineering of Advanced Materials (EAM) which made this collaboration possible.
